Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-09 paper.tex
Integrating Rich's text, and minor changes

\subsection*{Web services}

Web services offer a potentially powerful application of Open Source software,
particularly when combined with Open Data. For example, Metamolecular~\cite{Metamolecular}Metamolecular have released
gChem~\cite{gChem}, an Open Source library for Google Spreadsheets that enables
non-programmers to build and maintain chemically-aware spreadsheet documents
that can be easily shared and published. gChem makes use of the National Cancer Institute's
Chemical Identifier Resolver~\cite{ChemicalIdentifierResolver} to interconvert
substance names, database identifiers, SMILES and InChI codes, and to generate
embedded chemical structure images.

@@

At the time of writing there are many commercial companies development chemistry
solutions around Open Source cheminformatics components provided by the Blue Obelisk
community. Examples of such companies include iChemLabs, IdeaConsult, Wingu, Silicos,
GenettaSoft, hBar, Metamolecular, and Inkspot Science. Some of these merely use components, but several
actively contribute back to the Blue Obelisk project they use, or donate new
Open Source cheminformatics projects to the community.

>>>>

Web services offer a potentially powerful application of Open Source software,
particularly when combined with Open Data. For example, Metamolecular~\cite{Metamolecular}have released
gChem~\cite{gChem}, an Open Source library for Google Spreadsheets that enables
non-programmers to build and maintain chemically-aware spreadsheet documents
that can be easily shared and published. gChem makes use of the National Cancer Institute's
Chemical Identifier Resolver~\cite{ChemicalIdentifierResolver} to interconvert
substance names, database identifiers, SMILES and InChI codes, and to generate
embedded chemical structure images.

@@

At the time of writing there are many commercial companies development chemistry
solutions around Open Source cheminformatics components provided by the Blue Obelisk
community. Examples of such companies include iChemLabs, IdeaConsult, Wingu, Silicos,
GenettaSoft, eMolecules, hBar, Metamolecular, and Inkspot Science. Some of these merely use components, but several
actively contribute back to the Blue Obelisk project they use, or donate new
Open Source cheminformatics projects to the community.
